Algebra

### 2017-02-14 Algebra/Noetherian Ring.tex
[minor] Error correction.

\title{Noetherian Ring}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    A note about Noetherian Ring, majorly from the book \cite{lang}.
}
\tableofcontents

@@

\section{Noetherian}
\label{sec:Noetherian}
\begin{defi}[Noetherian Module]
    \nomenclature{Noetherian Module}{\nomrefpage.}
    Let $A$: a ring. $M$: a left $A$-module. $M$ is called Noetherian
    if $M$ satisfies any of the following conditions:
    \begin{enumerate}
        \item Every submodule of $M$ is finitely generated.
        \item Every ascending sequences of submodules of $M$
            \[ M_1 \subset M_2 \subset \cdots \]
            such that $M_i \neq M_{i+1}$, is fininte.
        \item Every non-empty set $S$ of submodules of $M$ has a maximal
            element.
    \end{enumerate}
\end{defi}

@@

\begin{coro}
    \label{coro:Noetherian.1.3}
    A finite direct sum of Noetherian modules is Noetherian. Specifically,
    let $M$ be a module, let $N,N'$ be two submodules. If $M=N+N'$ and if
    both $N,N'$ are Noetherian, then $M$ is Noetherian.
\end{coro}
(\textbf{pp.415 of \cite{lang}})
\begin{prop}
    \label{prop:Noetherian.1.4}
    Let $A$ be a Noetherian ring, and let $M$ be a finitely generated
    $A$-module. Then $M$ is Noetherian.
\end{prop}
(\textbf{pp.415 of \cite{lang}})
\begin{prop}
    \label{prop:Noetherian.1.5}
    Let $A$ be a ring which is Noetherian, and let $\phi:A\to B$ be
    a surjective ring-homomorphism. Then $B$ is Noetherian.
\end{prop}
(\textbf{pp.415 of \cite{lang}})
In colloquial term, a surjective homomorphism induces a Noetherian ring.
\begin{prop}
    \label{prop:Noetherian.1.6}
    Let $A$ be a commutative Noetherian ring, and let $S$ be a
    multiplicative subset of $A$. Then $S^{-1}A$ is Noetherian.
\end{prop}
(\textbf{pp.415 of \cite{lang}})
\section{Examples}
\label{sec:Examples}
\begin{itemize}
    \item The polynomial Ring
    \item The ring of power series
    \item The ring of formal power series is \textbf{NOT} Noetherian.
        See this \href{http://math.stackexchange.com/questions/281597/an-example-of-a-non-noetherian-ufd}{post}
        \begin{quote}
        The essential point is that the polynomial ring in infinitely many variables is the ascending union of subrings $K[x_1,\ldots,x_n]$, since any polynomial can involve only finitely-many indeterminates. Each of these rings is a UFD, and it is easy to see that a polynomial in which $x_N$ does not appear has only factorizations in which $x_N$ does not appear, again because everything takes place inside some polynomial ring in finitely-many variables. But the ring is not Noetherian, because the ideal generated by all the indeterminates is certainly not finitely-generated.
        \end{quote}
\end{itemize}
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\printnomenclature
\begin{thebibliography}{1}
    \bibitem{lang} S. Lang. Algebra. 3rd. Springer.
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

\title{Algebra}
\date{\today}
\author{we.taper}
\begin{document}
\maketitle
\abstract{
    A note about Abstract Algebra, majorly from the book \cite{lang}.
}
\tableofcontents

\section{Commutator}
\label{sec:Commutator}

A \nomen{commutator} in a group $G$ is a group element of the form
$xyx^{-1}y^{-1}$ with $x,y\in G$. Let \nomen{$G^c$} denote the
subgroup of $g$ generated by all its commutators. This is a group
because $xyx^{-1}y^{-1}aba^{-1}b^{-1}$

@@

\section{Noetherian Ring}
\label{sec:Noetherian}
\begin{defi}[Noetherian Module]
    \nomenclature{Noetherian Module}{\nomrefpage.}
    Let $A$: a ring. $M$: a left $A$-module. $M$ is called Noetherian
    if $M$ satisfies any of the following conditions:
    \begin{enumerate}
        \item Every submodule of $M$ is finitely generated.
        \item Every ascending sequences of submodules of $M$
            \[ M_1 \subset M_2 \subset \cdots \]
            such that $M_i \neq M_{i+1}$, is fininte.
        \item Every non-empty set $S$ of submodules of $M$ has a maximal
            element.
    \end{enumerate}
\end{defi}

@@

\begin{coro}
    \label{coro:Noetherian.1.3}
    A finite direct sum of Noetherian modules is Noetherian. Specifically,
    let $M$ be a module, let $N,N'$ be two submodules. If $M=N+N'$ and if
    both $N,N'$ are Noetherian, then $M$ is Noetherian.
\end{coro}
(\textbf{pp.415 of \cite{lang}})
\begin{prop}
    \label{prop:Noetherian.1.4}
    Let $A$ be a Noetherian ring, and let $M$ be a finitely generated
    $A$-module. Then $M$ is Noetherian.
\end{prop}
(\textbf{pp.415 of \cite{lang}})
\begin{prop}
    \label{prop:Noetherian.1.5}
    Let $A$ be a ring which is Noetherian, and let $\phi:A\to B$ be
    a surjective ring-homomorphism. Then $B$ is Noetherian.
\end{prop}
(\textbf{pp.415 of \cite{lang}})
In colloquial term, a surjective homomorphism induces a Noetherian ring.
\begin{prop}
    \label{prop:Noetherian.1.6}
    Let $A$ be a commutative Noetherian ring, and let $S$ be a
    multiplicative subset of $A$. Then $S^{-1}A$ is Noetherian.
\end{prop}
(\textbf{pp.415 of \cite{lang}})
    \subsection{Examples}
    \label{sec:Examples}
    \begin{itemize}
        \item The polynomial Ring
        \item The ring of power series
        \item The ring of formal power series is \textbf{NOT} Noetherian.
            See this
            \href{http://math.stackexchange.com/questions/281597/an-example-of-a-non-noetherian-ufd}{post}:
            \begin{quote}
            The essential point is that the polynomial ring in
            infinitely many variables is the ascending union of
            subrings $K[x_1,\ldots,x_n]$, since any polynomial can
            involve only finitely-many indeterminates. Each of these
            rings is a UFD, and it is easy to see that a polynomial in
            which $x_N$ does not appear has only factorizations in
            which $x_N$ does not appear, again because everything
            takes place inside some polynomial ring in finitely-many
            variables. But the ring is not Noetherian, because the
            ideal generated by all the indeterminates is certainly not
            finitely-generated.
            \end{quote}
    \end{itemize}
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\printnomenclature
\begin{thebibliography}{1}
    \bibitem{lang} S. Lang. Algebra. 3rd. Springer.
\end{thebibliography}
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.
